Final Project

### 2020-11-25 chaloupka_sameshima_wallner_final_project.Rmd
Add Presentation
added presentation .Rmd and updated writeup .Rmd with new/updated figures and such

## Fractal Iteration GIF

```{r}

library(magick)

Tree_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4nts3v.gif")

Fractal_Curve_C <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsf7.gif")

Sierpinski_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntsnw.gif")

Hilbert <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntswb.gif")

Pythagoras_A <- image_read("C:/Users/sgwallner/Downloads/r_projects/final_project/4ntt1q.gif")

Tree_A
Fractal_Curve_C
Sierpinski_A
Hilbert
Pythagoras_A

```

@@

seq_fractal_data %>% 
  ggplot(aes(x = sequence_position, y = dwell_time)) +
  facet_wrap(~fractal_type) +
  geom_point(data = new_data_forever, aes(y = mean_dwell_time)) +
  scale_y_continuous(limits = c(0, 1.2)) +
  labs(y = "Dwell Time (s)", x = "Sequence Position")
```

@@

```{r}
raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

raw_B_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point() +
  geom_smooth(method = "lm", se = F)

raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_line()

>>>>

@@

temp <- seq_fractal_data %>% 
  mutate(seq_pos2 = case_when(
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 18,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 17,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 16,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 15,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 14,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 13,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 12,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 11,
    direction == "Decay" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 10,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 1 ~ 1,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 2 ~ 2,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 3 ~ 3,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 4 ~ 4,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 5 ~ 5,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 6 ~ 6,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 7 ~ 7,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 8 ~ 8,
    direction == "Growth" & (fractal_type == "Fern_A" | fractal_type == "Fern_B") & sequence_position == 9 ~ 9,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 12,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 11,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 10,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 9,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 8,
    direction == "Decay" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 7,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 1 ~ 1,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 2 ~ 2,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 3 ~ 3,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 4 ~ 4,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 5 ~ 5,
    direction == "Growth" & (fractal_type == "Fractal_Curves_A" | fractal_type == "Fractal_Curves_B" | fractal_type == "Fractal_Curves_C" | fractal_type == "Fractal_Curves_D" | fractal_type == "Fractal_Curves_E" | fractal_type == "Hilbert" | fractal_type == "Moore" | fractal_type == "Sierpinski_B") & sequence_position == 6 ~ 6,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 1 ~ 16,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 2 ~ 15,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 3 ~ 14,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 4 ~ 13,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 5 ~ 12,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 6 ~ 11,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 7 ~ 10,
    direction == "Decay" & fractal_type == "Tree_A" & sequence_position == 8 ~ 9,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 1 ~ 1,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 2 ~ 2,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 3 ~ 3,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 4 ~ 4,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 5 ~ 5,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 6 ~ 6,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 7 ~ 7,
    direction == "Growth" & fractal_type == "Tree_A" & sequence_position == 8 ~ 8,
    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 10,
    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 9,
    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 8,
    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 7,
    direction == "Decay" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 6,
    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 1 ~ 1,
    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 2 ~ 2,
    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 3 ~ 3,
    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 4 ~ 4,
    direction == "Growth" & fractal_type == "Sierpinski_A" & sequence_position == 5 ~ 5,
    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 8,
    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 7,
    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 6,
    direction == "Decay" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 5,
    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 1 ~ 1,
    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 2 ~ 2,
    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 3 ~ 3,
    direction == "Growth" & (fractal_type == "Pythagoras_A" | fractal_type == "Pythagoras_B") & sequence_position == 4 ~ 4))

new_data_never <- temp %>% 
  group_by(seq_pos2, fractal_type) %>% 
  summarise(mean_dwell_time = round(mean(dwell_time), 3),
            sd_dwell_time = round(sd(dwell_time), 3))

temp %>% 
  ggplot(aes(x = seq_pos2, y = dwell_time, color = fractal_type)) +
  facet_wrap(~fractal_type) +
  geom_point(data = new_data_never, aes(y = mean_dwell_time)) +
  labs(y = "Dwell Time (s)", x = "Sequence Position", title = "Unfolding Dwell Times Over Sequential Fractal Iteration", subtitle = "by Fractal Type") +
  scale_y_continuous(limits = c(0, 1.4)) +
  geom_line(data = new_data_never, aes(y = mean_dwell_time)) +
  theme(legend.position = "none") +
  scale_color_viridis_d()

unique(seq_fractal_data$fractal_type)
```

@@

```{r}
raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = F) +
  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 1: Fractal Curves -> Tree Fractal", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")

raw_B_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_point(alpha = .6) +
  geom_smooth(method = "lm", se = F) +
  labs(title = "Unfolding Dwell Times Over Duration of Task", subtitle = "Group 2: Tree Fractal -> Fractal Curves", x = "Image Number (for entire task)", y = "Dwell Time (s)", color = "Participant")
```

```{r}
raw_A_long %>% 
  ggplot(aes(x = number, y = dwell_time, color = participant)) +
  geom_line()
